Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-08-19 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
	\begin{align*}
	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
	\qquad \bsk = (k_1, \ldots, k_d) \in \N_0^d,\\
    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
    \qquad \tu_{k}(x) := \cos( k \cos^{-1}(x)) \quad \forall k \in \N_0.
	\end{align*}
For this example, let $\calF$ denote a Hilbert space of input functions where we choose $\bbK=\bbN_0^d$ and $\rho=2$,
\begin{equation*}
    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
\end{equation*}
The $w_\ell$ are non-negative \emph{coordinate weights}, which embody the assumption that $f$ may depend more strongly on coordinates with larger $w_\ell$ than those with smaller $w_\ell$.  The definition of the $\calF$-norm implies that an input function must have series coefficients that decay quickly enough as the degree of the polynomial increases.  Larger $r$ implies smoother input functions.

@@

\DHKMchange{We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
\begin{equation} \label{DHKM:PilotConeNecessary}
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
\end{equation}
}

If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.  The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.

\DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.  An alternative might be to define a cone for which a weaker norm of the function provides an upper bound on the original norm.  Here is such a cone:
\begin{multline} \label{DHKM:altconedef}
    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{i}}{\lambda_{\bsk}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
\end{multline}
The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.  The following proposition describes how the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} are related.
\begin{proposition}
If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ satisfy
\[ 
\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho}
\le A \le \omega_{n_1} A'' \text{ and} \qquad  \omega_{n_1+1}A' < 1, 
\]
then 
\[
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
\subseteq 
\calC_{\boldsymbol{\lambda}, n_1, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}.
\]
\end{proposition}

\begin{proof}
Let us prove $
\calC_{\boldsymbol{\lambda}, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
Suppose $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
\begin{equation*}
    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
\end{equation*}
Thus, if $A\omega_{n_1}^{-1} \le A''$, i.e. $A \le \omega_{n_1} A'' $, then
we obtain $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So,

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{Fred got to here}
\YuhanNote{Create a new subsection and move the content related with the example here}
\DHKMchange{
Before we revisit the example in Section \ref{DHKM:secexamp}, we introduce several lemmas.

\begin{lemma}\label{DHKM:lambdineq}
Consider the ordered weights,
$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
then we have for $p>0$,
\[ \sum_{i=1}^\infty \lambda_{d,\bsk_{i}}^p \le \frac{1}{n^{1/p}}
\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p\right)^{1/p}\].
\end{lemma}
\PeterNote{It seems to me that on the left-hand side of the 
above inequality we need $\lambda_{\bsk_{n+1}}^p$, right?}
\begin{proof}
As $\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0$, we obtain for $p>0$
\begin{align*}
    n \lambda_{\bsk_{n+1}}^p & \le 
    \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \\
    \Longleftrightarrow 
    \lambda_{\bsk_{n+1}}&  \le \frac{1}{n^{1/p}}
\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \right)^{1/p}.
\end{align*}
\end{proof}

To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $w_1, \ldots, w_d$, and positive \emph{smoothness weights}, $s_1, s_2, \ldots$:
\begin{equation}
    \label{DHKM:prodwts}
\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN.
\end{equation}
To stress the dependence on $d$, we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$
  This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.

\begin{lemma}\label{DHKM:prodwtsupperbound}
Consider $\lambda_{d,\bsk}$ defined in \eqref{DHKM:prodwts},
we have for $p>0$,
\[\sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p \le \exp\left(\sum_{k=1}^\infty s_k^p \sum_{\ell = 1}^{d} w_\ell^{p} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^p \sum_{\ell = 1}^{\infty} w_\ell^{p} \right),\]
if $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite.
\end{lemma}
\begin{proof}
\begin{align*}
   \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  & =
   \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) \qquad \text{ by \eqref{DHKM:prodwts} }\\
    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \bigr) \right)\\
 &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
\qquad \text{since }\log(1+x) \le x \ \forall x\ge 0,\\
&\le \exp\left(\sum_{\ell = 1}^\infty w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
\qquad \text{ since  } \sum_{\ell = 1}^{\infty} w_\ell^{p} \text{ converges}.\\
\end{align*}
\end{proof}

The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$, $\rho' = \infty$. Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
\begin{align*}
	\COMP(\calA(\calB_{R}),\varepsilon,R) &= \COST(\ALG,\calB_{R},\varepsilon,R) 
	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
\end{align*}
Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $p^\text{th}$ power of all the $\lambda_{\bsk}$.  For $0  < 1/r < p$, by Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound} with $s_k = k^{-r}$, 
\begin{align*}
n\lambda_{\bsk_{n+1}}^{p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{p}  \le 
\exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}\frac{1}{k^{p r} }\right)
 \le \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right).
\end{align*}
Hence, substituting the above upper bound on $\lambda_{\bsk_{n+1}}$ into the formula for the complexity of the problem, we obtain an upper bound on the complexity:
\begin{align*}
    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} \\
  &\le\min\left\{ n \in \N_0 : \frac{1}{n}\exp\left(\zeta(p r) \sum_{\ell = 1}^\infty w_\ell^{p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{p}  \right\} \\
  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right) \right \rceil .
\end{align*}

If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$. On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
}

@@

Let's revisit the example in Section \ref{DHKM:secexamp}. For this example,
we choose $n_j = n_02^j,$ thus
\[\calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N \qquad \text{ and } \calK_1 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}.\]
For example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
\[\Lambda_j = \|(\lambda_\bsk)_\bsk \in \calK_j\|_{\rho'} = \lambda_{\bsk_{n_0 2^{j-1}+1}}.\]
By Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound}, we obtain
\[\Lambda_j \le \frac{1}{ n_0^{1/p} 2^{(j-1)/p}} \exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right),\]
where $0< 1/r< p$.
\begin{align*}
\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}^\tau
 & =  \sum_{q=1}^\infty
( b^{j+q}\Lambda_{j+q})^\tau \\
& \le \sum_{q=1}^\infty b^{(j+q)\tau} 
 \frac{1}{ n_0^{\tau/p} 2^{(j+q-1)\tau/p}} \exp\left(\frac{\tau}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)\\
& = 
\frac{\exp\left(\frac{\tau}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)}{ n_0^{\tau/p} } \sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}\\
\Leftrightarrow 
\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}
 & \le  \frac{\exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)}{ n_0^{1/p} } 
\left(\sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
\right)^{1/\tau}
\end{align*}
Therefore, the upper bound of the computation cost is $n_j^\dagger$, where
\[j^\dagger = \min \left \{j \in \bbN : 
\left(\sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
\right)^{1/\tau}
\le  \frac{b\varepsilon n_0^{1/p}}{Ra^2}\exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right) \right\}.\]
}

>>>>

Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
	\begin{align*}
	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
	\qquad \bsk = (k_1, \ldots, k_d) \in \N_0^d,\\
    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
    \qquad \tu_{k}(x) := \cos( k \cos^{-1}(x)) \quad \forall k \in \N_0.
	\end{align*}
For this example, let $\calF$ denote a Hilbert space of input functions where we choose $\bbK=\bbN_0^d$ and $\rho=2$,
\begin{multline}
\label{DHKM:IllExWts}
    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \\ \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
\end{multline}
The $w_\ell$ are non-negative \emph{coordinate weights}, which embody the assumption that $f$ may depend more strongly on coordinates with larger $w_\ell$ than those with smaller $w_\ell$.  The definition of the $\calF$-norm implies that an input function must have series coefficients that decay quickly enough as the degree of the polynomial increases.  Larger $r$ implies smoother input functions.

@@

\DHKMchange{We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
\begin{equation} \label{DHKM:PilotConeNecessary}
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
\end{equation}
}%
If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.  The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.

\DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.  An alternative is to define a cone for which a weaker norm of the function provides an upper bound on the original norm.  Here is such a cone:
\begin{multline} \label{DHKM:altconedef}
    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
\end{multline}
The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.  The following proposition describes how the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} are related.
\begin{proposition}
If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega} = (\omega_1, \omega_2, \ldots)$ satisfy
\[ 
\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho}
\le A \le \omega_{n_1} A'' \text{ and} \qquad  \omega_{n_1+1}A' < 1, 
\]
then the two types of cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} include one another:
\[
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
\subseteq 
\calC_{\boldsymbol{\lambda}, n_1, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}.
\]
\end{proposition}

\begin{proof}
Let us prove $
\calC_{\boldsymbol{\lambda}, n_1, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
If $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
\begin{equation*}
    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
\end{equation*}
Thus, if $A\omega_{n_1}^{-1} \le A''$, i.e. $A \le \omega_{n_1} A'' $, then
we must have $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So, $
\calC_{\boldsymbol{\lambda}, n_1, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\YuhanNote{Create a new subsection and move the content related with the example here}
\DHKMchange{
We now interpret the information cost upper bounds of Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} for the example introduced in Section \ref{DHKM:secexamp}, where $\rho = \tau = 2$ and $\rho' = \infty$.  In this case, $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$.  To facilitate this interpretation we establish a couple of commonly used lemmas.

\begin{lemma}\label{DHKM:lambdineq}
Consider the ordered weights,
$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
then we have
\[ 
\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \qquad \forall p >0,
\]
provided that $\norm[p]{\bslambda}$ is finite.
\end{lemma}
\begin{proof}
Since the $\lambda_{\bsk_i}$ are non-increasing it follows that 
\begin{equation*}
    n \lambda_{\bsk_{n+1}}^p \le 
    \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK}^\infty \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
\end{equation*}
Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof.
\end{proof}

To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $\bsw = (w_1, \ldots, w_d)$, and positive \emph{smoothness weights}, $\bss = (s_1, s_2, \ldots)$:
\begin{equation}
    \label{DHKM:prodwts}
\lambda_{\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \bbK :=\NN_0^d, \ d \in \NN.
\end{equation}
This is a generalization of our illustrative example, \eqref{DHKM:IllExWts}, in Section \ref{DHKM:secexamp} where $\bss = (1, 2^{-r}, 3^{-r}, \ldots )$.  
This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.

\begin{lemma}\label{DHKM:prodwtsupperbound}
For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
we have 
\begin{align*}
\norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
 \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
\end{align*}
\end{lemma}
\begin{proof}
The proof proceeds by straightforward calculation under the assumption that $\norm[p]{\bss}$ is finite:
\begin{align*}
   \norm[p]{\bslambda}^ p & 
   = \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
   \qquad \text{ by \eqref{DHKM:prodwts} }\\
    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
 &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
\quad \text{since }\log(1+x) \le x \ \forall x\ge 0.
\end{align*}
Taking the $p^{\text{th}}$ root completes the proof for the general case.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
\end{proof}

Lemmas \ref{DHKM:lambdineq} and \ref{DHKM:prodwtsupperbound} imply upper bounds on $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$:
\begin{align*}
\lambda_{\bsk_{n+1}} &\le \frac{1}{n^{1/p}} \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
\lambda_{\bsk_{n+1}} & \le \frac{1}{n^{1/p}} \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \  \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
\end{align*}
These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
\begin{equation*}
    \text{Algorithm \ref{DHKM:BallAlg}:} \quad \COST(\ALG,\calB_R,\varepsilon, R') 
    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil,
    \end{equation*}
    \begin{multline*}
    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
    \\ \le \max \left( n_1, 
    \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
    \end{multline*}
Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$. A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients implies smaller information cost.
}

\FredNote{Fred got to here}

\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obatain lower bounds on the computational complexity. }

@@

Let's revisit the example in Section \ref{DHKM:secexamp}. For this example,
we choose $n_j = n_02^j,$ thus
\[\calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N \qquad \text{ and } \calK_1 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}.\]
For example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
\[\Lambda_j = \|(\lambda_\bsk)_\bsk \in \calK_j\|_{\rho'} = \lambda_{\bsk_{n_0 2^{j-1}+1}}.\]
By Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound}, we obtain
\[\Lambda_j \le \frac{1}{ n_0^{1/p} 2^{(j-1)/p}} \exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right),\]
where $0< 1/r< p$.
\begin{align*}
\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}^\tau
 & =  \sum_{q=1}^\infty
( b^{j+q}\Lambda_{j+q})^\tau \\
& \le \sum_{q=1}^\infty b^{(j+q)\tau} 
 \frac{1}{ n_0^{\tau/p} 2^{(j+q-1)\tau/p}} \exp\left(\frac{\tau}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)\\
& = 
\frac{\exp\left(\frac{\tau}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)}{ n_0^{\tau/p} } \sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}\\
\Leftrightarrow 
\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}
 & \le  \frac{\exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right)}{ n_0^{1/p} } 
\left(\sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
\right)^{1/\tau}
\end{align*}
Therefore, the upper bound of the computation cost is $n_j^\dagger$, where
\[j^\dagger = \min \left \{j \in \bbN : 
\left(\sum_{q=1}^\infty 
\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
\right)^{1/\tau}
\le  \frac{b\varepsilon n_0^{1/p}}{Ra^2}\exp\left(\frac{1}{p}
\zeta(pr)\sum_{\ell=1}^\infty 
w_\ell^p
\right) \right\}.
\]
}
